Pillar 1 - Sequential Pattern Mining

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd

subsequences <- sequences %>%
  cspade(
    parameter = list(
      support = 0.2, # min support of a sequence
      maxsize = 1, # max number of items of an element of a sequence
      maxlen  = 2, # max number of element of a sequence
      mingap  = 1, # min time difference between consecutive element of a sequence
      maxgap  = 1e4, # max time difference between consecutive element of a sequence
      maxwin  = 1e4  # max time difference between any two elements of a sequence
      ),
    control = list(
      verbose = FALSE
      )
    )

@@

  separate(rule, into=c("LHS", "RHS"), sep = "=>", remove = T) %>% #remove = F to keep columns

@@

##calculate appropriate measures:
```{r}
n_students <- length(unique(d_sequence_transactions$`Student ID`))

>>>>

subsequences <- sequences %>%
  cspade(
    parameter = list(
      support = 0.01, # min support of a sequence
      maxsize = 1, # max number of items of an element of a sequence
      maxlen  = 2, # max number of element of a sequence
      mingap  = 1, # min time difference between consecutive element of a sequence
      maxgap  = 1e4, # max time difference between consecutive element of a sequence
      maxwin  = 1e4  # max time difference between any two elements of a sequence
      ),
    control = list(
      verbose = FALSE
      )
    )

@@

  separate(sequece, into=c("LHS", "RHS"), sep = "=>", remove = T) %>% #remove = F to keep columns

@@

# Transform AR from apriori into a readable data frame
clean_rules <- function(rules){
  rules %>%
    as("data.frame") %>%
    # filter(
    #   count >= 1
    # ) %>%
    mutate(
      rule = str_remove(rule, pattern = "[<]"),
      rule = str_remove(rule, pattern = "[{]"),
      rule = str_remove(rule, pattern = "[}]"),
      rule = str_remove(rule, pattern = "[>]"),
      rule = str_remove(rule, pattern = "[<]"),
      rule = str_remove(rule, pattern = "[{]"),
      rule = str_remove(rule, pattern = "[}]"),  #this is repeated, because it only removes the first instance
     # rule = str_remove(rule, pattern = "[>]"), #this is taken out because the rules is marked with a => so it removes that one. 
      `rhs.support` = confidence / lift
    ) %>%
    separate(rule, into = c("lhs", "rhs"), sep="=>") %>%
    mutate(
      lhs = str_remove(rule, pattern = "[<]"),
      lhs = str_remove(rule, pattern = "[{]"),
      lhs = str_remove(rule, pattern = "[}]"),
      lhs = str_remove(rule, pattern = "[>]"),
      rhs = str_remove(rule, pattern = "[<]"),
      rhs = str_remove(rule, pattern = "[{]"),
      rhs = str_remove(rule, pattern = "[}]"),
      rhs = str_remove(rule, pattern = "[>]")
    ) %>%
    mutate_at(
      c("support", #"lhs.support",
        "confidence", "rhs.support", "lift"),
      funs(round(., 5))
    ) %>%
    select(
      lhs, rhs,
      support, #count, lhs.support,
      confidence, rhs.support,
      lift
    ) #%>%
    #arrange(
    #  desc(count)
    #)

}
```
##calculate appropriate measures:
```{r}
n_students <- length(unique(d_sequence_transactions$`Student ID`))
